Outdated and License-Violating Code on Stack Overflow

### 2017-02-27 cloneoverflow-latex/cloneoverflow.tex
Small changes to the abstract.

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter
  315,786,118 detected online clone pairs between 144,064 Java code
  snippets on Stack Overflow and 111 Java open source projects in the
  curated Qualitas corpus. We discovered and investigated 32,533
  non-trivial online clone candidates. Our study revealed that 64 out
  of 112 clones with strong evidence of copying from a Qualitas
  project to Stack Overflow are outdated. Furthermore, we found 357
  code snippets on Stack Overflow that violate the license of their
  original software.
  % These snippets are questionable for reuse.
  % Our study is among the first to address the problem of
  % outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

%FIXME: We probably have to discuss IN clones.
%FIXME: the numbers where 28,642 and 2,529 which I could not find elsewhere.
\textbf{To answer RQ2, we found that a large amount of the clone pairs
  between Stack Overflow and Qualitas projects are boiler-plate code
  (29,330) or accidental clones (2,420) with no evidence that the code
  has actually been copied. Nevertheless, we found 112 pairs that had
  strong evidences to be cloned from Qualitas to Stack Overflow and
  200 pairs were found to be cloned to Stack Overflow from external
  sources outside Qualitas projects.} 
%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}

@@

\textbf{Internal validity:} 
%
We could not verify all the 315,786,118 clone pairs reported by the
clone detection tools in this study.  Nevertheless, we applied
different mechanisms to ensure the validity to the subset of clone
pairs we classified.  First, we used two widely-used
clone detection tools, Simian and NiCad.  We tried three other
clone detectors but could not add them to the study due to their
scalability issues and susceptibility to incomplete code snippets.
Second, we adopted Bellon's agreement metric~\cite{Bellon2007}
to prioritise and filters clone pairs for the manual
classification. The agreed clone pairs that passed \textit{good}- and
\textit{ok}- criteria had a higher chance to be true positive. 
Nevertheless, we might still suffers from false negatives, i.e.~online 
code clones that are not reported by the tools or are filtered 
out by the automatic classifier before the manual investigation.
% We also
% applied the Bellon's clone agreement to 4 different combinations of
% the tools' configurations.  For disagreed clone pairs, we applied
% several filters to remove spurious and uninteresting clones.

% The number of online clones we found are subject to the clone
% detectors and their configurations.  
We mitigated the problem of clone
detector's parameter sensitivity by adding another established
configuration from the EvaClone study~\cite{Wang2013}.

@@

The 3,636 clone pairs classified manually by the first author are
subject to manual judgement and human errors.  Although we have tried
our best to be careful on searching for evidence and classifying the
clones, some errors may still exist. We mitigated this problem by
having the second author to validate the classifications with a random
sampling. 
% The 64 classification conflicts were discussed and
% resolved.  
The third author made a final judgement when no consensus
could be found by the two authors. This validation process
can be even improved by employing an external investigator. 
 %In addition, we are aware of voting mechanism
%in Stack Overflow and plan to incorporate highest-vote answers in the future work.

@@

\textbf{Reusing of outdated third-party source code} occurs 
in software development. Xia et al.~\cite{Xia2014} show that 
a large number of open source systems reuse outdated third-party 
libraries from popular open source projects. Using the outdated 
code give detrimental effects to the software since they may 
introduce vulnerabilities. Our study discovers similar findings 
in the context of outdated code on Stack Overflow.

>>>>

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter detected
  online clone pairs between 144,064 Java code snippets on Stack
  Overflow and 111 Java open source projects in the curated Qualitas
  corpus. We discovered and analysed 32,533 non-trivial online clone
  candidates. Our investigation of 3,636 manually confirmed clone
  pairs revealed strong evidence that 112 clones have been copied from
  a Qualitas project to Stack Overflow.  We found 64 of them (57\%) 
  to be outdated and potentially harmful for reuse.  Furthermore, we
  found 357 code snippets on Stack Overflow that violate the license
  of their original software.
  % These snippets are questionable for reuse.
  % Our study is among the first to address the problem of
  % outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

%FIXME: We probably have to discuss IN clones.
%FIXME: the numbers where 28,642 and 2,529 which I could not find elsewhere.
\textbf{To answer RQ2, we found that a large amount of the clone pairs
  between Stack Overflow and Qualitas projects are boiler-plate code
  (29,330) or accidental clones (2,420) with no evidence that the code
  has actually been copied. Nevertheless, we found 112 pairs that had
  strong evidences to be cloned from Qualitas to Stack Overflow and
  200 pairs were found to be cloned to Stack Overflow from external
  sources.} 
%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}

@@

\textbf{Internal validity:} 
%
We could not verify all the 315,786,118 clone pairs reported by the
clone detection tools in this study.  Nevertheless, we applied
different mechanisms to ensure the validity to the subset of clone
pairs we classified.  First, we used two widely-used
clone detection tools, Simian and NiCad.  We tried three other
clone detectors but could not add them to the study due to their
scalability issues and susceptibility to incomplete code snippets.
We mitigated the problem of clone
detector's parameter sensitivity by adding another established
configuration from the EvaClone study~\cite{Wang2013}. 
Second, we adopted Bellon's agreement metric~\cite{Bellon2007}
to prioritise and filters clone pairs for the manual
classification. The agreed clone pairs that passed \textit{good}- and
\textit{ok}- criteria had a higher chance to be true positive. 
Nevertheless, we might still suffers from false negatives, i.e.~online 
code clones that are not reported by the tools or are filtered 
out by the automatic classifier before the manual investigation.
% We also
% applied the Bellon's clone agreement to 4 different combinations of
% the tools' configurations.  For disagreed clone pairs, we applied
% several filters to remove spurious and uninteresting clones.

% The number of online clones we found are subject to the clone
% detectors and their configurations.

@@

The 3,636 clone pairs classified by the first author are
subject to manual judgement and human errors.  Although we tried
our best to be careful on searching for evidence and classifying the
clones, some errors may still exist. We mitigated this problem by
having the second author to validate the classifications with a random
sampling. 
% The 64 classification conflicts were discussed and
% resolved.  
The third author made a final judgement when no consensus
could be found by the two authors. This validation process
can be even improved by employing an external investigator. 
 %In addition, we are aware of voting mechanism
%in Stack Overflow and plan to incorporate highest-vote answers in the future work.

@@

\textbf{Reusing of outdated third-party source code} occurs 
in software development. Xia et al.~\cite{Xia2014} show that 
a large number of open source systems reuse outdated third-party 
libraries from popular open source projects. Using the outdated 
code give detrimental effects to the software since they may 
introduce vulnerabilities. Our study similarily finds
% on % the context of 
outdated code on Stack Overflow.
